\mireval{}: A Transparent Implementation of Common MIR Metrics

### 2014-07-02 paper/paper.tex
Unredacting

While we have given thorough consideration to the design choices made in \mireval{}, we recognize that standards change over time, new metrics are proposed each year, and that only a subset of MIR tasks are currently implemented in \mireval{}.
Towards this end, \mireval{} is hosted on Github,\footnote{URL redacted} which provides a straightforward way of proposing changes and additions to the codebase using the Pull Request feature.
With active community participation, we believe that \mireval{} can ensure that MIR research converges on a standard methodology for evaluation.

@@

The authors would like to thank (name redacted) for helpful advice about comparing chord labels.

>>>>

While we have given thorough consideration to the design choices made in \mireval{}, we recognize that standards change over time, new metrics are proposed each year, and that only a subset of MIR tasks are currently implemented in \mireval{}.
Towards this end, \mireval{} is hosted on Github,\footnote{\url{http://github.com/craffel/mir_eval}} which provides a straightforward way of proposing changes and additions to the codebase using the Pull Request feature.
With active community participation, we believe that \mireval{} can ensure that MIR research converges on a standard methodology for evaluation.

@@

The authors would like to thank Matthew McVicar for helpful advice about comparing chord labels.
